Observed vs. Simulated Year Comparison

### 2023-06-02 03-post-process/compare-sim-to-obs.Rmd

For us to use the state-space model as a simulation model (which is the ultimate intent), it would be desirable if several characteristics of the distribution of stochastic and derived quantities were similar between the time periods with and without observations.

@@

Several quantities are supplied to the model as known without error in the observed time series (weir removals, hatchery smolt releases, harvest rates below BON, etc.). These time series were extended to the future years external to the model using basic averages or resampling from historical outcomes as appropriate. This exercise is purely for model validation.

@@

If these summary statistics are inconsistent among the observed and simulated time periods, that indicates that the state-space model has not sufficiently captured the random processes that have generated the observed outcomes and that we may have reason to question the reliability of its ability to simulate future outcomes, at least as a direct extension of the historical population dynamics.

@@

The entire 1991 - 2019 period isn't used for the observed period because the early years did not have a hatchery program but the simulation has hatchery input in all years. Thus, including the non-hatchery years may throw off the inference.

>>>>

For us to use output from the state-space model to parameterize simulation models, it would be desirable if several features of the distribution of stochastic and derived quantities were similar between the time periods with and without observations.

@@

Several quantities are supplied to the model as known without error in the observed time series (weir removals, hatchery smolt releases, harvest rates below BON, etc.).
These time series were extended to the future years external to the model by simply duplicating the time series and "tacking it on".
This exercise is purely for model validation, so we deemed this simple approach suitable.

@@

@@

The entire 1991 -- `r all_yrs[max(obs_y)]` period isn't used for the observed period because the early years did not have a hatchery program.

### 2023-06-02 03-post-process/output-plots-children/08-misc-processes.Rmd

## Correction for Carcass Age Bias

 {.tabset .tabset-pills}

@@

## CAT

```{r p-Sa-prime-plots-CAT, fig.width = p6_width, fig.height = p6_height}
# loop over age/origin combos for CAT
mypar(mfrow = c(2,3))
junk = sapply(1:jags_data$nko, function(ko) plot_f(j = j_cat, ko = ko))
axis_labels("Brood Year", "% Composition")
```

## LOS

```{r p-Sa-prime-plots-LOS, fig.width = p6_width, fig.height = p6_height}
# loop over age/origin combos for CAT
mypar(mfrow = c(2,3))
junk = sapply(1:jags_data$nko, function(ko) plot_f(j = j_los, ko = ko))
axis_labels("Brood Year", "% Composition")
```

## MIN

```{r p-Sa-prime-plots-MIN, fig.width = p6_width, fig.height = p6_height}
# loop over age/origin combos for CAT
mypar(mfrow = c(2,3))
junk = sapply(1:jags_data$nko, function(ko) plot_f(j = j_min, ko = ko))
axis_labels("Brood Year", "% Composition")
```

## UGR

```{r p-Sa-prime-plots-UGR, fig.width = p6_width, fig.height = p6_height}
# loop over age/origin combos for CAT
mypar(mfrow = c(2,3))
junk = sapply(1:jags_data$nko, function(ko) plot_f(j = j_ugr, ko = ko))
axis_labels("Brood Year", "% Composition")
```

>>>>

## Correction for Carcass Age Bias {.tabset .tabset-pills}

@@

### CAT

```{r p-Sa-prime-plots-CAT, fig.width = p6_width, fig.height = p6_height}
# loop over age/origin combos for CAT
mypar(mfrow = c(2,3))
junk = sapply(1:jags_data$nko, function(ko) plot_f(j = j_cat, ko = ko))
axis_labels("Brood Year", "Proportion of Spawners")
```

### LOS

```{r p-Sa-prime-plots-LOS, fig.width = p6_width, fig.height = p6_height}
# loop over age/origin combos for CAT
mypar(mfrow = c(2,3))
junk = sapply(1:jags_data$nko, function(ko) plot_f(j = j_los, ko = ko))
axis_labels("Brood Year", "Proportion of Spawners")
```

### MIN

```{r p-Sa-prime-plots-MIN, fig.width = p6_width, fig.height = p6_height}
# loop over age/origin combos for CAT
mypar(mfrow = c(2,3))
junk = sapply(1:jags_data$nko, function(ko) plot_f(j = j_min, ko = ko))
axis_labels("Brood Year", "Proportion of Spawners")
```

### UGR

```{r p-Sa-prime-plots-UGR, fig.width = p6_width, fig.height = p6_height}
# loop over age/origin combos for CAT
mypar(mfrow = c(2,3))
junk = sapply(1:jags_data$nko, function(ko) plot_f(j = j_ugr, ko = ko))
axis_labels("Brood Year", "Proportion of Spawners")
```

### 2023-06-02 03-post-process/output-plots-children/13-post-vs-prior.Rmd

  # function to plot one population/pair
  plot_f = function(j) {
    post_v_prior(
      post_samps = post_subset(post, sub_index(post_param, pop = j, ...), matrix = TRUE),
      prior_samps = post_subset(post, sub_index(prior_param, pop = j, ...), matrix = TRUE),
      label_text = titles[j], 
      legend_loc = ifelse(j == looping[1], legend_loc, NA),
      y_max = y_max,
      xlim = xlim
    )
  }

@@

```{r}
# set these figure options for all plots in this section
y_max = 0.15
xlim = c(-1,1)
knitr::opts_chunk$set(fig.width = p4_height, fig.height = p4_width, out.width = "50%")
```

>>>>

  # function to plot one population/pair
  plot_f = function(j) {
    post_v_prior(
      post_samps = post_subset(post, sub_index(post_param, pop = j, ...), matrix = TRUE),
      prior_samps = post_subset(post, sub_index(prior_param, pop = j, ...), matrix = TRUE),
      label_text = titles[which(looping == j)], 
      legend_loc = ifelse(j == looping[1], legend_loc, NA),
      y_max = y_max,
      xlim = xlim
    )
  }

@@

```{r}
# set these figure options for all plots in this section
y_max = 0.15
xlim = c(-1,1)
knitr::opts_chunk$set(fig.width = p4_height * 1.1, fig.height = p4_width, out.width = "50%")
```
